Behavior Driven Development in Haskell

### 2012-05-28 paper.tex
evidences -> evidence.
label and ref.

In BDD, all behavior should be documented, together with some
\emph{evidence}\/s for that behavior.
For this purpose, 
we brought a test method from other programming language community and
extended missing features.
In particular, we introduced Doctest~\cite{doctest} and
integrated it with QuickCheck~\cite{quickcheck}
for user documentation.
For code documentation,
we make use of Hspec inspired by RSpec~\cite{rspec}
and we proposed some combinators to it.

@@

\begin{itemize}
\item
    Implement Doctest in Haskell and add support for QuickCheck properties to Doctest (Section
    \ref{sec:for-users} and Section \ref{sec:doctest})

\item
    Introduce a set of combinators to set expectations about
    code examples (simply ``code'' hereafter) for use with Hspec. (Section \ref{sec:for-developers})

@@

\begin{itemize}
\item
    The Haskell community does not have common syntax to describe
    evidence with Haddock markup syntax.
\item
    The Haskell community does not have a BDD tool for
    evidence for users.
\item
    Hspec does not provide combinators to express expectations with
    BDD terminology
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evidence for users}
\label{sec:for-users}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evidence for developers}

@@

\subsection{Hspec combinators for expectations}

>>>>

In BDD, all behavior should be documented, together with some
\emph{evidence} for that behavior.
For this purpose, 
we brought a test method from other programming language community and
extended missing features.
In particular, we introduced Doctest~\cite{doctest} and
integrated it with QuickCheck~\cite{quickcheck}
for user documentation.
For code documentation,
we make use of Hspec inspired by RSpec~\cite{rspec}
and we proposed some combinators to it.

@@

\begin{itemize}
\item
    Implement Doctest in Haskell and add support for QuickCheck properties to Doctest (Section
    \ref{sec:user-doc} and Section \ref{sec:doctest})

\item
    Introduce a set of combinators to set expectations about
    code examples for use with Hspec. (Section \ref{sec:code-doc} and Section \ref{sec:hspec-comb})

@@

\begin{itemize}
\item
    The Haskell community does not have common syntax to describe
    evidence with Haddock markup syntax.
\item
    The Haskell community does not have a BDD tool for user documentation.
\item
    Hspec does not provide combinators to express expectations with
    BDD terminology
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{User documentation}
\label{sec:user-doc}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Code documentation}
\label{sec:code-doc}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Hspec combinators for expectations}
\label{sec:hspec-comb}
